---
title: "R Notebook"
output: html_notebook
---

1 MVP
1.1 Local PostgreSQL connections
```{r}
library(keyring)
library(RPostgreSQL)


username <- key_get(service = "postgresql_username", keyring = "local")
password <- key_get(service = "postgresql_password", keyring = "local")
keyring_lock(keyring = "local")


my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 1), user = username, password = password, dbname = 'wrestling', host='localhost')
rm(username)
rm(password)
```

```{r}

dbListTables(conn = my_db_connection)
dbListFields(conn = my_db_connection, name = "wrestlers")


```

```{r}
dbGetQuery(my_db_connection,
           "SELECT * FROM wrestlers")
```


id = integer
born = character
name = character
gender = character
win_percent = double
total matches = integer






2 Extensions

Return all the details for any wrestlers from the United Kingdom
```{r}
dbGetQuery(my_db_connection,
           "SELECT * FROM wrestlers
           WHERE born = 'United Kingdom'")
```

Get the names of all Japanese wrestlers who have appeared in 40 or more matches
```{r}
dbGetQuery(my_db_connection,
           "SELECT * FROM wrestlers
           WHERE total_matches >= 40 AND born = 'Japan'")
```


Find the wrestlers who have won between 50% and 60% of their matches.
```{r}
dbGetQuery(my_db_connection,
           "SELECT * FROM wrestlers
           WHERE win_percent BETWEEN 50 AND 60")
```

Find all the wrestlers with names beginning with ‘X’
```{r}
dbGetQuery(my_db_connection,
           "SELECT * FROM wrestlers
           WHERE name LIKE 'X%'")
```


Find all the wrestlers who were born in countries beginning with the letter ‘I’. Try this using IN (there are 9 countries) and using a wildcard comparison.
```{r}
dbGetQuery(my_db_connection,
           "SELECT * FROM wrestlers
           WHERE born LIKE 'I%'")
```







Find all the wrestlers who were not born in countries beginning with the letter ‘I’
```{r}
dbGetQuery(my_db_connection,
           "SELECT * FROM wrestlers
           WHERE born NOT LIKE 'I%'")
```

























```{r}
dbDisconnect(my_db_connection)
```


1.2 Remote PostgreSQL connections
```{r}
#keyring_create(keyring = "remote")
key_set(service = "wrestling_postgresql_username", keyring = "remote")

key_set(service = "wrestling_postgresql_password", keyring = "remote")

keyring_lock(keyring = "remote")
```


```{r}
```







```{r}
username <- key_get(service = "wrestling_postgresql_username", keyring = "remote")
password <- key_get(service = "wrestling_postgresql_password", keyring = "remote")
keyring_lock(keyring = "remote")

db_connect <- dbConnect(drv = PostgreSQL(max.con = 1), user = username, password = password, dbname = 'mvhbdgdk', host = '34.245.37.126')
```


```{r}
dbDisconnect(my_db_connection)
```


```{r}
library(keyring)
keyring_create(remote)
```































