---
title: "R Notebook"
output: html_notebook
---

```{r}
library(RPostgreSQL)
library(keyring)

```

```{r}
keyring_unlock(keyring = "local")
```

```{r}
username <- key_get(service = "postgresql_username", keyring = "local")
password <- key_get(service = "postgresql_password", keyring = "local")
keyring_lock(keyring = "local")

```

```{r}
my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 1), user = username, password = password, dbname="acme_employees", host="localhost")
rm(username)
rm(password)
```


```{r}
dbListTables(conn = my_db_connection)
```

```{r}
dbListFields(conn = my_db_connection, name = "employees")
```
```{r}
dbListFields(conn = my_db_connection, name = "teams")
```

```{r}
dbListFields(conn = my_db_connection, name = "feedbacks")
```




Create a new data.frame containing the details of all employees held in the database
```{r}
dbGetQuery(my_db_connection,
           "SELECT * FROM employees")
```


Retrieve the records for all employees again, but this time add a field full_name containing the first_name and last_name of each employee separated by a space.
```{r}
dbGetQuery(my_db_connection,
           "SELECT id, first_name, last_name, 
           CONCAT(first_name, ' ', last_name) AS full_name
           FROM employees")
```


Retrieve the details of all employees again, but this time listing their team name (as team_name), rather than their team_id.
```{r}
dbGetQuery(my_db_connection,
           "SELECT e.id, e.first_name, e.last_name, e.email, t.name AS team_name FROM employees AS e
           INNER JOIN teams AS t ON e.team_id = t.id")
```


Do a breakdown of the number of employees per team (here we want two columns: team_name and num_employees). Order the table in decreasing number of employees. Include all teams, even if they have no employees.

```{r}
dbGetQuery(my_db_connection,
           "SELECT COUNT(e.id) AS num_employees, t.name AS team_name
           FROM employees AS e INNER JOIN teams AS t
           ON e.team_id = t.id
           ORDER BY e.id DESC
           GROUP BY team_name")
```









```{r}
dbDisconnect(my_db_connection)
```



APIs


```{r}
library(httr)
library(jsonlite)
library(purrr)
library(keyring)
```

```{r}
keyring_unlock("remote_api2")
key_set("indico_api_key")
keyring_lock("remote_api2")
```

```{r}
keyring_unlock("remote_api2")
key_get("indico_api_key")
keyring_lock("remote_api2")
```





Write a get_emotions_from_indico_api() function that takes in api_key, url and message, POSTs the message to the Indico emotions endpoint, and returns the content(response). Try your function out one-by-one on the following two trial messages, and investigate the structure of the response contents:

messages <- c("I really like working here, great place, decent perks", "Hmm, not so sure I'll stay: long working hours and low pay, bad morale")

```{r}
get_emotions_from_indico_api <- function(emotions) {
  query_params <- list(ApiKey = indico_api_key, data = "I really like working here, great place, decent perks!")
                             response <- GET("https://apiv2.indico.io/sentiment", query = query_params)
                             content(response)
        
}
```


```{r}
get_emotions_from_indico_api2 <- function(emotions) {
  query_params <- list(ApiKey = indico_api_key, data = "I really like working here, great place, decent perks!")
                             response <- GET("https://apiv2.indico.io/emotion", query = query_params)
                             content(response)
}
```









```{r}
GET("https://apiv2.indico.io/emotion")
```













