---
title: "NHS Borders Analysis"
author: "Amber Lawther"
date: "19/12/2019"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r results='hide', echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(readr)
library(knitr)
library(janitor)
```


```{r results='hide', echo=FALSE, warning=FALSE, message=FALSE}
all_regions <- read_csv("opendata_inc9317_hb2018.csv")

borders_cancer <- all_regions %>%
  filter(HBR2014 == "S08000016")



borders_clean <- clean_names(borders_cancer)


all_types <- borders_clean %>%
  select(cancer_site, sex, year, incidences_all_ages, crude_rate) %>%
  filter(cancer_site == "All cancer types",
         sex == "All")

by_type <- borders_clean %>%
  select(cancer_site, sex, year, incidences_all_ages, crude_rate) %>%
  filter(cancer_site != "All cancer types",
         sex == "All") %>%
  group_by(cancer_site)%>%
  arrange(desc(crude_rate))

NHS_dkblue <- "#002d72"
NHS_ltblue <- "#00a9e0"

NHS_palette <- c(NHS_dkblue, NHS_ltblue, "black")

male_female_1993 <- borders_clean %>%
  select(cancer_site, sex, year, incidences_all_ages) %>%
  filter(cancer_site != "All cancer types",
         year == 1993,
         sex != "All") %>%
  rename(mf_year_1993 = year,
         mf_incidences_1993 = incidences_all_ages)

male_female_2017 <- borders_clean %>%
  select(cancer_site, sex, year, incidences_all_ages) %>%
  filter(cancer_site != "All cancer types",
         year == 2017,
         sex != "All") %>%
  rename(mf_year_2017 = year,
         mf_incidences_2017 = incidences_all_ages)

male_female_1993to2017 <- male_female_1993 %>%
  inner_join(male_female_2017)

male_female_increase <- male_female_1993to2017 %>%
  ungroup() %>%
  mutate(mf_incidence_change = mf_incidences_2017 - mf_incidences_1993) %>%
  arrange(desc(mf_incidence_change)) %>%
  top_n(10)

mf_site_percent_increase <- male_female_increase %>%
  mutate(mf_percent_increase = mf_incidence_change/mf_incidences_1993 * 100) 

male_female_decrease <- male_female_1993to2017 %>%
  mutate(mf_incidence_change = mf_incidences_2017 - mf_incidences_1993) %>%
  arrange(mf_incidence_change) %>%
  slice(1:10)

mf_site_percent_decrease <- male_female_decrease %>%
  mutate(mf_percent_decrease = mf_incidence_change/mf_incidences_1993 * 100)



```

# Incidence of Cancer in NHS Borders

### Initial look at overall incidences to determine if there is an apparent trend






```{r, echo=FALSE}
all_types_plot <- all_types %>%
  ggplot() +
  geom_point(aes(x = year, y = incidences_all_ages), colour = NHS_dkblue) +
  geom_line(aes(x = year, y = incidences_all_ages), colour = NHS_dkblue) +
  labs(
    x = "\nYear\n\n",
    y = "Incidences of Cancer\n",
    title = "\n\nAll Cancer Types from 1993 to 2017\n"
    )
  
all_types_plot
```

> The graph displays an increasing trend in the overall incidence of cancer in NHS Borders.






#### The next step was to subtract 1993 incidences from 2017 incidences to portray the cancer sites with 
#### the largest increase between the two years.






```{r, echo=FALSE}
mf_increase_plot <- male_female_increase %>%
  ggplot(aes(x = cancer_site, y = mf_incidence_change, fill = sex)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = NHS_palette) +
  labs(
    x = "Incidence Change\n",
    y = "\nCancer Site\n\n",
    title = "\n\nIncrease in Incidences between 1993 and 2017\n",
    fill = "Sex") +
  theme(plot.title = element_text(size = 11))

mf_increase_plot
```

> This graph shows that skin cancers make up some of the largest incidence changes between 1993 and 2017.






#### The information was corroborated by plotting line graphs, which illustrated an overall increase from
#### 1993 to 2017, and also by plotting graphs which showed the increase in incidences without the breakdown of sex.






```{r, echo=FALSE}
mf_percent_increase_plot <- mf_site_percent_increase %>%
  ggplot(aes(x = cancer_site, y = mf_percent_increase, fill = sex)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = NHS_palette) +
  labs(
    x = "Incidence Percent Increase\n",
    y = "\nCancer Site\n\n",
    title = "\n\nPercent Increase in Incidences between 1993 and 2017\n",
    fill = "Sex") +
  theme(plot.title = element_text(size = 10))
  
mf_percent_increase_plot
```

> The percent increases were calculated to compare with the previous graph






#### The largest decreases between 1993 and 2017, along with the percent decreases, were also calculated
#### and visualised, which can be seen in the following graphs.






```{r, echo=FALSE}
male_female_decrease_plot <- male_female_decrease %>%
  ggplot(aes(x = cancer_site, y = mf_incidence_change, fill = sex)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = NHS_palette) +
  labs(
    x = "Incidence Change\n",
    y = "\nCancer Site\n\n",
    title = "\n\nDecrease in Incidences between 1993 and 2017\n",
    fill = "Sex") +
  theme(plot.title = element_text(size = 11))
  
male_female_decrease_plot
```






```{r, echo=FALSE}
mf_percent_decrease_plot <- mf_site_percent_decrease %>%
  ggplot(aes(x = cancer_site, y = mf_percent_decrease, fill = sex)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = NHS_palette) +
  labs(
    x = "Incidence Percent Decrease\n",
    y = "\nCancer Site\n\n",
    title = "\n\nPercent Decrease in Incidences between 1993 and 2017\n",
    fill = "Sex") +
  theme(plot.title = element_text(size = 10))
  
mf_percent_decrease_plot
```








