---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
data(msleep)
```

```{r}
library(infer)
```

```{r}
view(msleep)
```


Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.



Null hypothesis: The mean sleep_total of sampled animal types does not differ from the mean sleep value of jabberwockies.
  H(0): μ(sleep_total) = 7

Alternative hypothesis:  The mean sleep_total of sampled animals types differs from the mean sleep value of jabberwockies.
  H(a): μ(sleep_total) != 7
  
  α = 0.05
  
```{r}
observed_stat <- msleep %>%
  summarise(mean_sleep = mean(sleep_total))
observed_stat
```
  
```{r}
msleep %>%
ggplot(aes(x = sleep_total)) +
geom_histogram(bins = 30)
```


```{r}
msleep %>%
ggplot(aes(y = sleep_total)) +
  geom_boxplot() +
  coord_flip()
  
```

```{r}
null_distribution <- msleep %>%
  specify(response = sleep_total) %>%
  hypothesize(null = "point", mu = 7) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")

null_distribution
```

```{r}
null_distribution %>%
  visualise(bins = 30)
```


```{r}
null_distribution %>%
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat, direction = "both")
```

```{r}
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "both")
p_value
```
Reject the null hypothesis.



Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

```{r}
msleep_tidy <- msleep %>%
  drop_na()
msleep_tidy
```


```{r}
omni_vs_herbi <- msleep_tidy %>%
  mutate(omni_herbi = case_when(vore == "omni" ~ "omni",
                                vore == "herbi" ~ "herbi")) %>%
  select(omni_herbi, sleep_total) %>%
drop_na()
omni_vs_herbi
  
```


null hypothesis:  Omnivores do not sleep longer than herbivores.
  H(0): μ(sleep)omni - μ(sleep)herbi = 0

alternative hypothesis: Omnivores sleep longer than herbivores
  H(a): μ(sleep)omni - μ(sleep)herbi > 0
  
α = 0.05

```{r}
omni_vs_herbi %>%
  group_by(omni_herbi) %>%
  summarise(n = n())
```

```{r}
omni_vs_herbi %>%
  ggplot(aes(y = sleep_total, x = omni_herbi)) +
  geom_boxplot()
```

```{r}
null_distribution_oh <- omni_vs_herbi %>%
  specify(sleep_total ~ omni_herbi) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
head(null_distribution_oh)
```


```{r}
observed_stat <- omni_vs_herbi %>% 
  specify(sleep_total ~ omni_herbi) %>%
  calculate(stat = "diff in means", order = c("omni", "herbi"))
  
observed_stat
```


```{r}
null_distribution_oh %>%
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "right")
```


```{r}
p_value <- null_distribution_oh %>%
  get_p_value(obs_stat = observed_stat, direction = "right")

p_value
```

Fail to reject the null hypothesis.




Perform an appropriate statistical test to determine whether the proportion of domesticated animals in the population of animal types is greater than 5%.

null hypothesis: the proportion of domesticated animals is not greater than 5%
   H(0) : p(domesticated) !> 0.05
  
alternative hypothesis: the proporition of domesticated animals is greater than 5 %.
  H(a) : p(domesticated) > 0.05
  
α=0.05
  
  
```{r}
domesticated_animals <- msleep %>%
  mutate(domesticated_flag = ifelse(conservation == "domesticated",
                                    "domesticated", 
                                    "not_domesticated"))
  
           
                              
                                         
  

domesticated_animals


```
  
  


```{r}
null_distribution_domesticated <- domesticated_animals %>%
  specify(response = domesticated_flag, success = "domesticated") %>% 
  hypothesize(null = "point", p = 0.05) %>%
  generate(reps = 10000, type = "simulate") %>%
  calculate(stat = "prop")
head(null_distribution_domesticated)
```

```{r}
null_distribution_domesticated %>%
  visualise()
```

```{r}
observed_stat_domesticated <- domesticated_animals %>% 
  specify(response = domesticated_flag, success = "domesticated") %>% 
  calculate(stat = "prop")

observed_stat
```



```{r}
null_distribution_domesticated %>%
  visualise() +
shade_p_value(obs_stat = observed_stat_domesticated, direction = "right")
```



```{r}
p_value <- null_distribution_domesticated %>%
  get_p_value(obs_stat = observed_stat_domesticated, direction = "right")

p_value
```


reject the null hypothesis.

I know something went wrong in this problem.  I tried a few different ways to change the NAs, but I just couldn't get it to work.  Went ahead with the problem anyway, just to get the practice of working through it.






