---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library
```



MVP

1. Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.



```{r}
tweets <- read_csv("code_clan_tweets.csv")
view(tweets)
```

```{r}
dim(tweets)
```
 
```{r}
names(tweets)
```
 


2. First, we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.

```{r}
tweets %>%
summarise(count = sum(is.na(favorite_count)))
```


```{r}
summary(tweets$favorite_count)

```



```{r}
boxplot(tweets$favorite_count)
```





3. Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).


```{r}
favorite_sum <- tweets %>%
  filter(is_quote == FALSE) %>%
  summarise(tweet_likes = sum(favorite_count)) 
  
   
```

```{r}
favorite_sum
```


4. Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.


```{r}
tweets %>%
  group_by(source) %>%
  filter(is_quote == FALSE) %>%
  summarise(mean_retweets = mean(retweet_count)) 
  
```
































